---
title: "HW 9"
author: "Hannah Lim"
date: "2025-04-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(ggplot2)
library(mosaic)
library(tidyverse)
library(kableExtra)
library(effectsize)
library(moderndive)


boards = read.csv('solder.csv')
groceries = read.csv('groceries.csv')
```

## UT EID:
hl33387

## GitHub Link:
https://github.com/hannahlim506/HW-9

## Problem 1: Manufacturing Flaws in Circuit Boards
Part A: Make two plots. The first plot should provide evidence that the size of the opening on the solder gun is related to the number of skips. The second should provide evidence that the thickness of the alloy used for soldering is related to the number of skips. Give each plot an informative caption describing what is shown in the plot.

```{r}
# Part A:
ggplot(boards) + 
  geom_boxplot(aes(x=Opening, y=skips)) +
  labs( x = "Opening Size", 
        y = "Number of Skips", 
        caption = "The median for number of skips for each opening size increases as the opening size decreases.\n The median number of skips for the large opening is 0 while the median for the small opening is 8 skips.\n The range for the number of skips for the small opening is bigger than the large opening and the max skips collected is 48 skips.\n This shows that the opening size influences the number of skips.", 
        title = "Size of the Opening vs. Number of Skips")

ggplot(boards) + 
  geom_boxplot(aes(x=Solder, y=skips)) +
  labs( x = "Solder Thickness", 
        y = "Number of Skips",
        caption = "The median for the number of skips for the thin solder is higher than it is for the thick solder.\n The range is also bigger for the this solder, the max number of skips being 48 skips.\n This shows that the thickness of the solder influences the number of skips.",
        title = "Solder Thickness vs. Number of Skips")
```


Part B: 
```{r}
# Part B:
model_boards <- lm(skips ~ Opening + Solder + Opening:Solder, data = boards)

get_regression_table(model_boards, conf.level = 0.95, digits=2)

```

Part C:
The baseline skips for boards with large openings and a thick solder is 0. The main effect for the opening medium size variable is 2, while the opening small size variable is 5. These are the effect of OpeningM and OpeningS in isolation respectively. The main effect for the Solder variable is 68 skips, and it is the effect of solder in isolation. The interaction effect for OpeningM and SolderThin is -1 skips. This means that boards that have both medium sized openings and a thin solder yield average skips that is one less than what is expected from summing the individual "isolated" effectings of the two variables. The effect of OpeningS and SolderThin, which was 10 skips, shows that in boards that have small sized openings and a thin solder will yield average skips that is 10 skips more than what is expected for the isolated effects of the variables.

Part D:
If I had to recommend a combination of Opening size and Solder thickness to AT&T based on this analysis, it would be the large opening and the thick solder. This is because the predicted skips is 0. As the opening gets smaller, the skips increase, as it does with a thin solder as well.


## Problem 2: Grocery Store Prices

Part A:

```{r}
avg_price_by_store <- groceries %>%
  group_by(Store) %>%
  summarize(avg_price = mean(Price, na.rm = TRUE))

ggplot(avg_price_by_store, aes(x = avg_price, y = reorder(Store, avg_price))) +
  geom_bar(stat = "identity") +
  labs(
    x = "Average Price",
    y = "Store",
    title = "Average Product Prices by Store",
    caption = "Stores are sorted by average price. Whole Foods has the highest average price while Fiesta has the lowest."
    ) + 
  coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
```

Part B.

```{r}
products_by_store <- groceries %>%
  distinct(Store, Product, City) %>%
  count(Product, name = "num_stores")

ggplot(products_by_store, aes(x = num_stores, y = reorder(Product, num_stores))) +
  geom_bar(stat = "identity") +
  labs( x = "Number of Stores Selling Product",
        y = "Product",
        title = "Availability of Each Product Across Stores",
        caption = "Eggs and milk are sold in all 16 stores; other products vary."
      ) + 
  theme(axis.text.y = element_text(size = 7))
```

Part C.
Compared with ordinary grocery stores (like Albertsons, HEB, or Krogers), convenience stores charge somewhere between $5.45 and $6.40 dollars more for the same product.

```{r}
model_groceries <- lm(Price ~ Product + Type, data = groceries)
summary(model_groceries)
confint(model_groceries)
```

Part D.
Walmart and Kroger Fresh Fare seem the charge the lowest prices when comparing the same product.
Wheatsville Food Co-Op and Whole Foods seem to charge the highest prices when comparing the same product.

```{r}
model_store <- lm(Price ~ Product + Store, data = groceries)
coef(summary(model_store))
```

Part E.
Central Market charges more than HEB for the same product. This can be seen in the coefficients from the fitted model. Central Market had a coefficient of -0.5734 while HEB had a coefficient fo -0.6459. This shows that there is a difference between HEB and Central Market, however this difference is not compared to differences among other stores, using Whole Foods as an example, which had a coefficient of 0.3642.

```{r}
coef(model_store)["StoreCentral Market"]
coef(model_store)["StoreH-E-B "]

```

Part F.
The coefficient for the Income10K on Price is negative. This means consumers in poorer ZIP codes seem to pay more for the same product on average or higher-income ZIP codes pay less for the same product on average. This means that for every $10,000 increase in income, the price decreases by $0.01, on average for the same product.
A one-standard deviation increase in the income of a ZIP code seems to be associated with a -0.03 standard-deviation change in the price that consumers in that ZIP code expect to pay for the same product.

```{r}
income <- groceries %>%
  mutate(Income10K = Income / 10000)

model_income <- lm(Price ~ Product + Income10K, data = income)
summary(model_income)

standardize_parameters(model_income)
```
 
## Problem 3:
